---
title: "You're a data scientist? Blog about it!"
subtitle: "MEDS 2021-22"
author: "Sam Csik"
date: "Fall 2021"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    seal: false
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width = 9, fig.height = 3.5, fig.retina = 3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include = FALSE, warning = FALSE}
# load package
library(xaringanthemer)

# set accent theme
style_mono_accent(
  header_font_google = google_font("Sanchez"), 
  text_font_google = google_font("Glacial Indifference", "300", "300i"),
  code_font_google = google_font("Fira Mono"),
  base_color = "#05859B",
  white_color = "#93C6C2",
  background_color = "#FFFFFF",
  header_font_weight = 400,
  header_h1_font_size = "2.25rem",
  header_h2_font_size = "1.75rem",
  header_h3_font_size = "1.5rem",
  footnote_font_size = "0.7em",
)
```

class: inverse, middle

# You're a data scientist? Blog about it!<br>

<br>

<span style = 'font-size: 130%;'>Sam Csik | Data Training Coordinator</span>  

National Center for Ecological Analysis & Synthesis<br>

<br>

<span style = 'font-size: 130%;'>Masters of Environmental Data Science | Fall 2021</span>   

Slides & source code available on [`r fontawesome::fa("github", fill = "#93C6C2", a11y = "sem")`](https://github.com/UCSB-MEDS/writing-blogposts)

---

# I made my first blog post 🎉

.center[
*And I'm here to tell you why you should too.*
]

.center[
```{r, out.width = '70%', echo = FALSE}
knitr::include_url("https://samanthacsik.github.io/posts/2021-09-21-my-first-test-post/")
```
]

---

# Why blog?

--
* Build your online profile/portfolio 
    
    * **"...sharing *anything* is almost always better than sharing nothing."** -[@drob](https://twitter.com/drob) in his post, [Advice to aspiring data scientists: start a blog](http://varianceexplained.org/r/start-blog/)

--
* Practice writing & communication skills  

--
* Stay atop DS trends  


--
* Solicit feedback from the community  


--
* Network<sup>1</sup>  

.footnote[
<sup>1</sup>Real people have gotten real jobs because the right person noticed their blog post at the right time. Lucky for sure, but not unheard of!
]

--
* Learn something new and/or solidify understanding   


--
* Combat imposter syndrome  
   
    * **"Once you've shared some analyses and code, you'll probably find that you were underrating yourself in some areas."** also -[@drob](https://twitter.com/drob) in his post, [Advice to aspiring data scientists: start a blog](http://varianceexplained.org/r/start-blog/)


---
# Contribute to the MEDS Community Blog!

[Scout Leonard](https://scoutcleonard.github.io/) & [Juliet Cohen](https://julietcohen.github.io/) published our first student-authored MEDS blog post this week:

.center[
```{r, out.width = '70%', echo = FALSE}
knitr::include_url("https://ucsb-meds.github.io/posts/2021-09-24-summery-summary/")
```
]

---
# Explore other data science blogs

* [The Distillery: Showcase](https://distillery.rbind.io/showcase.html) (collection of `{distill}` blogs - you can even add yours!)

* [Kara Woo](https://blog.karawoo.com/): senior data science engineer at InsightRX (and NCEAS alum)

* [Julia Silge](https://juliasilge.com/blog/): data scientist & software engineer at RStudio

* [David Robinson](http://varianceexplained.org/about/): principle data scientist at HEAP

* [Vicki Boykis](http://veekaybee.github.io/): machine learning engineer at Tumblr

* [Chelsea Parlett-Pelleriti](https://cmparlettpelleriti.github.io/writing.html): Assistant Prof at Chapman University & stats consultant

* [R-bloggers](https://www.r-bloggers.com/): a blog aggregator of content contributed by bloggers who write about R

.footnote[
This is by no means an exhaustive list. [Twitter](https://twitter.com/home?lang=en) is also a great place to find cool people blogging about cool data science stuff.
]
---
# Customizing your blog posts

Check out my [blog post](https://samanthacsik.github.io/posts/2021-09-21-my-first-test-post/) for details on how to do the following: 

1. Adding a preview image

2. Assigning posts to categories

3. Adding a table of contents

4. Creating citeable blog posts

5. Adding a bibliography

6. Adding an appendix